ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/evaluation.tex

\noindent\textbf{Summary.} We demonstrated that it is possible to achieve
networks with good accuracy when using ShrinkNets both when the network space
cannot be explored entirely (\texttt{CIFAR10}) as well as when it can, e.g.,
\texttt{COVERTYPE}. The most important result is not that ShrinkNets finds
networks of good accuracy, but that those networks are much smaller than those
found by a static method. The impact of the network size on inference time is
the subject of our next evaluation goal.

@@

ShrinkNets effectively explores the frontier of model size and accuracy. For a
given target accuracy, the size needed is significantly smaller than when we use the
"channel doubling" heuristic commonly used to size convolutional neural networks.
This suggests that this conventional heuristic may not in fact be optimal,
especially when looking for smaller models.  Empirically we observed this to
often be the case.  For example, during our experimentations on the
\texttt{MNIST} \cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017}
datasets (not reported here due to space constraints), we observed that even
though these datasets have the same number of classes, input features, and
output distributions, for a fixed $\lambda$ \textit{ShrinkNets} converged to
considerably bigger networks in the case of \texttt{FashionMNIST}. This evidence
shows that optimal architecture not only depends on the output distribution or
shape of the data but actually reflects the dataset.  This makes sense, as
\texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.

>>>>

%\srm{Summarize more quantitatively -- best model performance, model performance
%drop off for a factor of 10 reduction in seize, etc. so that we can repeat a
%quantitative claim in the intro, i.e., ``Here, the best performing ShrinkNets
%models has 9x.x\% accuracy while the best static model has 9x.x\% accuracy,
%while the ShrinkNets model is x times smaller.  Further, note that ShrinkNets
%finds a model with 9x.x\% accuracy that is y times than the best performing
%model.  Also, as on CIFAR10, if we give up just 1\% error, ShrinkNets finds a
%model that is z times smaller.'' (If we do this, would be good to highlight
%these points in the figure somehow)}

\subsubsection{Summary}

We  demonstrated that it is possible to achieve networks with good accuracy
when using ShrinkNets both when the network space cannot be explored entirely
(\texttt{CIFAR10}) and when it can, e.g., \texttt{COVERTYPE}. The most important
result is not that ShrinkNets finds networks of good accuracy, but that those
networks are much smaller than those found by a static method. The impact of the
network size on inference time is the subject of our next evaluation goal.

@@

\ra{the following is interesting, but how is it related to the above?}
ShrinkNets effectively explores the frontier of model size and accuracy. For a
given target accuracy, the size needed is significantly smaller than when we use the
"channel doubling" heuristic commonly used to size convolutional neural networks.
This suggests that this conventional heuristic may not in fact be optimal,
especially when looking for smaller models.  Empirically we observed this to
often be the case.  For example, during our experimentations on the
\texttt{MNIST} \cite{Lecun1998} and \texttt{FashionMNIST} \cite{Xiao2017}
datasets (not reported here due to space constraints), we observed that even
though these datasets have the same number of classes, input features, and
output distributions, for a fixed $\lambda$ \textit{ShrinkNets} converged to
considerably bigger networks in the case of \texttt{FashionMNIST}. This evidence
shows that optimal architecture not only depends on the output distribution or
shape of the data but actually reflects the dataset.  This makes sense, as
\texttt{MNIST} is a much easier problem than \texttt{FashionMNIST}.

### 2018-02-09 paper/ICML/paper.tex

\begin{abstract}
As neural networks become widely deployed in different applications and 
on different
hardware, it has become increasingly important to optimize inference time and
model size along with model accuracy.  
Most current techniques optimize model size,
model accuracy and inference time in different stages, resulting in suboptimal
results and computational inefficiency.  
In this work, we propose a new
technique called \shrink that optimizes all three of these metrics
simultaneously.  
Specifically we present a new method to simultaneously optimize network size and
model performance by neuron-level pruning during training.  
Neuron-level pruning not only
produces much smaller networks for a given accuracy threshold but also produces
dense weight matrices that are amenable to efficient inference.  
By applying our
technique to convolutional as well as fully connected models, we show that 
\shrink can reduce network size by 35X with a 6X improvement in inference time.
In addition, the most accurate networks found by \shrink have accuracy that is
similar to or better than those found by statically-sized networks.  
\end{abstract}

>>>>

\begin{abstract}
As neural networks become widely deployed in different applications and 
on different
hardware, it has become increasingly important to optimize inference time and
model size along with model accuracy.  
Most current techniques optimize model size,
model accuracy and inference time in different stages, resulting in suboptimal
results and computational inefficiency.  
In this work, we propose a new
technique called \shrink that optimizes all three of these metrics
simultaneously.  
Specifically we present a new method to simultaneously optimize network size and
model performance by neuron-level pruning during training.  
Neuron-level pruning not only
produces much smaller networks for a given accuracy threshold but also produces
dense weight matrices that are amenable to efficient inference.  
By applying our
technique to convolutional as well as fully connected models, we show that 
\shrink can reduce network size by 35X with a 6X improvement in inference time with similar accuracy as models found by traditional training techniques.

%By applying our technique to convolutional as well as fully connected models, we show that  \shrink can reduce network size by 35X with a 6X improvement in inference time. In addition, the most accurate networks found by \shrink have accuracy that is similar to or better than those found by statically-sized networks.  
\end{abstract}
